Investigating soundscapes perception through acoustic scenes simulation

### 2018-09-04 v2/responseToReviewers.tex

\documentclass[10pt]{article}
\usepackage{url}

\title{Reply to academic editor and reviewer concerning submission BR-Org-18-034 "Investigating soundscapes perception through acoustic scenes simulation"}

@@

\begin{document}

\maketitle

As a preamble, we would like to thank the editor and the reviewer for their comments and suggestions. Following these comments, we made several changes to the article, which are summarized here. The next sections list our answers to each of their comments, with references to the revised manuscript where appropriate.

@@

\item \emph{please follow APA (American Psychological Association) style guidelines (w.r.t. in-text citations, etc.).}

$\rightarrow$ The manuscript now follows the APA citation style. The text has been modified accordingly.

\item \emph{ Please avoid the over-use of acronyms as it makes reading of your article unnecessarily difficult (examples: P@5, ni, i, etc.). This sort of lab jargon is not transparent to the wider readership of BRM. }

$\rightarrow$ Those abbreviations are now in full text, except in for some figures for the sake of clarity, in which case the used acronyms are detailed in the caption.

@@

\item \emph{I would also like to see comparisons between your approach and other state-of-the-art soundscape analyses (e.g. TAPESTREA, see comment from the reviewer below).}

$\rightarrow$ The work of Misra \& al is indeed very relevant. A new Section (number 6) is now dedicated to this comparison with state-of-the-art approaches.

\item \emph{You might consider providing a link to a github site with examples of your stimuli. It is hard to imagine what these sound scenes sound like without some real examples.}

$\rightarrow$ The resulting waveforms are available for download \url{https://archive.org/details/soundSimulatedUrbanScene}. The link is now in the introduction. The software platform used for the experiment, the parametrization of the software platform for each generated scene, as well as a 2 dimensional projection of the resulting scenes are available at \url{http://soundthings.org/research/urbanSoundScape/XP2014}.

@@

\section{Answer to Reviewer}

\begin{enumerate}

\item \emph{The utility of this tool beyond the experiments presented here is not apparent because the flexibility of the system was not demonstrated, for example:
- SimScene itself was only used in the first experiment, and other applications of it were not considered. Design choices vary widely between researchers and domains, meaning that the specific instantiations here may not be generally useful.}

$\rightarrow$ We definitely agree. As now discussed in more detail in Section 6 of the manuscript, the proposed software tool is not designed for genericity but we believe that the proposed specific design strategies and use of recent software toolkits can be considered as inspirations for designing other experimental protocols questioning soundscape perception.

### 2018-09-05 lafaySimulatedScenePerception.tex
GL dernière relecture

\begin{enumerate}
\item \emph{experiment 1.a, simulation}:  the subjects use the soundscape simulator to produce ideal / non-ideal soundscapes that are considered as material for the following experiments (the resulting waveforms are available for download\footnote{Soundscapes, available online \url{https://archive.org/details/soundSimulatedUrbanScene}});
\item \emph{experiment 1.b, pleasantness evaluation}: the subjects judge the pleasantness of the simulated scenes on a semantic scale;
\item \emph{experiment 2, pleasantness evaluation after modification of the scenes}: the subjects judge the pleasantness of the simulated scenes on a semantic scale as in 1.b, but some scenes are modified beforehand, \ie~some specific sounds classes that are identified as having a significant impact on perceived pleasantness are removed.
\end{enumerate}

@@

In our approach, the simulator developed for this study\footnote{simScene, available online \url{https://bitbucket.org/mlagrange/simscene}} only yields a monophonic representation of the scene, but that simplification comes with the benefit of a wider range of available sound sources and scheduling parameters in order to provide outputs which are both expressive and useful for analysis.

@@

\emph{Simscene} is an online digital audio tool whose first version has been developed as part of the HOULE project\footnote{\emph{Projet HOULE} : \url{houle.ircam.fr}}. It has been designed to run on the popular web browsers \emph{Chrome} and \emph{Firefox}. It is fully written in javascript using the \emph{angular.js} library\footnote{\emph{angular.js} : \url{angularjs.org}} and the \emph{Web Audio} standard that allows the manipulation of digital audio data within the browser\footnote{\emph{Web Audio}: \url{www.w3.org/TR/webaudio}}. The interface for selecting sound sources (\cf~Section~\ref{sec:simscene_ssf}) uses the popular \emph{D3.js} visualization library proposed by~\cite{d32011}.

@@

Accounting for the previously detailed perceptual matters, two taxonomies are built, one for sound events and one for sound textures. Up to four levels of abstraction are considered from the most generic classes (level 0) to the most specific classes (level 3), leading to a taxonomy close to the one used in~\cite{Salamon14}, see Appendix~\ref{app:taxonomie}. Only three levels of abstraction are considered for the texture sounds, see Figure~\ref{fig:taxonomieT}.

@@

Among the 44 subjects, 40 succeeded, producing in the end 80 simulated sound scenes (40 ideal scenes, 40 non-ideal scenes). The 4 other subjects were excluded from the process due to a lack of understanding of the instructions or failure to respect them, or for exceeding the maximum duration allowed to perform the experiment.  The software platform used for the experiment, the parametrization of the software platform for each generated scene, as well as a 2 dimensional projection of the resulting scenes are available online\footnote{Available online \url{http://soundthings.org/research/urbanSoundScape/XP2014}}.

@@

\begin{figure}[!hp]
    \centering
        {\includegraphics[trim={ 0 0 0cm 1cm},clip,width=.9\columnwidth]{gfx/appendix/event_1_en}\label{fig:taxonomieEventa}} \par
         \caption{Taxonomy of sound classes of mechanical events used for the simulation urban soundscapes with level of abstraction from left to right.}
       \label{fig:taxonomieEa}
\end{figure}

\begin{figure}[hp]
    \centering
        {\includegraphics[trim={ 0 0 0cm 1cm},clip,width=.9\columnwidth]{gfx/appendix/event_2_en}\label{fig:taxonomieEventb}}
       \caption{Taxonomy of sound classes of non-mechanical events used for the simulation urban soundscapes with level of abstraction from left to right.}
       \label{fig:taxonomieEb}
\end{figure}

@@

        {\includegraphics[trim={ 0 0 7cm 1cm},clip,width=.7\columnwidth]{gfx/appendix/texture_2_en}\label{fig:taxonomieTextureb}}
       \caption{Taxonomy of sound classes of textures used for the simulation urban soundscapes with level of abstraction from left to right.}
       \label{fig:taxonomieT}
\end{figure}

@@

\begin{figure}[h]
        \myfloatalign
        \subfloat[subject 1]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_1}\label{fig:xp4_note_1a}}
        \subfloat[subject 2]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_2}\label{fig:xp4_note_1b}}
        \subfloat[subject 3]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_3}\label{fig:xp4_note_1c}}
        \subfloat[subject 4]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_4}\label{fig:xp4_note_1d}} \par
        \subfloat[subject 5]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_5}\label{fig:xp4_note_1e}}
        \subfloat[subject 6]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_6}\label{fig:xp4_note_1f}}
        \subfloat[subject 7]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_7}\label{fig:xp4_note_1g}}
        \subfloat[subject 8]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_8}\label{}} \par
        \subfloat[subject 9]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_9}\label{fig:xp4_note_1i}}
        \subfloat[subject 10]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_10}\label{fig:xp4_note_1j}}
        \subfloat[subject 11]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_11}\label{fig:xp4_note_1z}}
        \subfloat[subject 12]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_12}\label{fig:xp4_note_1l}}
        \caption{Distribution of scores given by the subjects during experiment 2 for the ideal scenes with markers (green) et non-ideal scenes with markers (red). The horizontal axis is, from left to right, the 11-point bipolar semantic scale ranging from -5 (non-ideal / very unpleasant) to +5 (ideal / very pleasant).}\label{fig:xp4_note_1}
\end{figure}

>>>>

\begin{enumerate}
\item \emph{experiment 1.a, simulation}:  the subjects use the soundscape simulator to produce ideal / non-ideal soundscapes that are considered as material for the following experiments (the resulting waveforms are available for download\footnote{Soundscapes: \url{https://archive.org/details/soundSimulatedUrbanScene}});
\item \emph{experiment 1.b, pleasantness evaluation}: the subjects judge the pleasantness of the simulated scenes on a semantic scale;
\item \emph{experiment 2, pleasantness evaluation after modification of the scenes}: the subjects judge the pleasantness of the simulated scenes on a semantic scale as in 1.b, but some scenes are modified beforehand, \ie~some specific sounds classes that are identified as having a significant impact on perceived pleasantness are removed.
\end{enumerate}

@@

In our approach, the simulator developed for this study\footnote{simScene: \url{https://bitbucket.org/mlagrange/simscene}} only yields a monophonic representation of the scene, but that simplification comes with the benefit of a wider range of available sound sources and scheduling parameters in order to provide outputs which are both expressive and useful for analysis.

@@

\emph{Simscene} is an online digital audio tool whose first version has been developed as part of the HOULE project\footnote{\emph{HOULE project}: \url{houle.ircam.fr}}. It has been designed to run on the popular web browsers \emph{Chrome} and \emph{Firefox}. It is fully written in javascript using the \emph{angular.js} library\footnote{\emph{angular.js}: \url{angularjs.org}} and the \emph{Web Audio} standard that allows the manipulation of digital audio data within the browser\footnote{\emph{Web Audio}: \url{www.w3.org/TR/webaudio}}. The interface for selecting sound sources (\cf~Section~\ref{sec:simscene_ssf}) uses the popular \emph{D3.js} visualization library proposed by~\cite{d32011}.

@@

Accounting for the previously detailed perceptual matters, two taxonomies are built, one for sound events and one for sound textures. Up to four levels of abstraction are considered from the most generic classes (level 0) to the most specific classes (level 3), leading to a taxonomy close to the one used in~\cite{Salamon14}, see~\ref{app:taxonomie}. Only three levels of abstraction are considered for the texture sounds, see Figure~\ref{fig:taxonomieT}.

@@

Among the 44 subjects, 40 succeeded, producing in the end 80 simulated sound scenes (40 ideal scenes, 40 non-ideal scenes). The 4 other subjects were excluded from the process due to a lack of understanding of the instructions or failure to respect them, or for exceeding the maximum duration allowed to perform the experiment.  The software platform used for the experiment, the parametrization of the software platform for each generated scene, as well as a 2 dimensional projection of the resulting scenes are available online\footnote{Experiment 1.a: \url{http://soundthings.org/research/urbanSoundScape/XP2014}}.

@@

\begin{figure}[!hp]
    \centering
        {\includegraphics[trim={ 0 0 0cm 1cm},clip,width=.9\columnwidth]{gfx/appendix/event_1_en}\label{fig:taxonomieEventa}} \par
         \caption{Taxonomy of sound classes of mechanical events used for the simulation of urban soundscapes, with level of abstraction from left to right.}
       \label{fig:taxonomieEa}
\end{figure}

\begin{figure}[hp]
    \centering
        {\includegraphics[trim={ 0 0 0cm 1cm},clip,width=.9\columnwidth]{gfx/appendix/event_2_en}\label{fig:taxonomieEventb}}
       \caption{Taxonomy of sound classes of non-mechanical events used for the simulation of urban soundscapes, with level of abstraction from left to right.}
       \label{fig:taxonomieEb}
\end{figure}

@@

        {\includegraphics[trim={ 0 0 7cm 1cm},clip,width=.7\columnwidth]{gfx/appendix/texture_2_en}\label{fig:taxonomieTextureb}}
       \caption{Taxonomy of sound classes of textures used for the simulation of urban soundscapes, with level of abstraction from left to right.}
       \label{fig:taxonomieT}
\end{figure}

@@

\begin{figure}[h]
        \myfloatalign
        \subfloat[subject 1]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_1}\label{fig:xp4_note_1a}}
        \subfloat[subject 2]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_2}\label{fig:xp4_note_1b}}
        \subfloat[subject 3]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_3}\label{fig:xp4_note_1c}}
        \subfloat[subject 4]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_4}\label{fig:xp4_note_1d}} \par
        \subfloat[subject 5]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_5}\label{fig:xp4_note_1e}}
        \subfloat[subject 6]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_6}\label{fig:xp4_note_1f}}
        \subfloat[subject 7]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_7}\label{fig:xp4_note_1g}}
        \subfloat[subject 8]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_8}\label{}} \par
        \subfloat[subject 9]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_9}\label{fig:xp4_note_1i}}
        \subfloat[subject 10]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_10}\label{fig:xp4_note_1j}}
        \subfloat[subject 11]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_11}\label{fig:xp4_note_1z}}
        \subfloat[subject 12]
        {\includegraphics[width=.24\linewidth]{gfx/appendix/xp4_note_12}\label{fig:xp4_note_1l}}
        \caption{Distribution of scores given by the subjects during experiment 2 for the ideal scenes with markers (green) and the non-ideal scenes with markers (red). The horizontal axis is, from left to right, the 11-point bipolar semantic scale ranging from -5 (non-ideal / very unpleasant) to +5 (ideal / very pleasant).}\label{fig:xp4_note_1}
\end{figure}
